Estimation of flow trajectories in a multi-lines network

### 2023-02-07 latex_files/applied_network_science_article/article_v0.tex
ajouter étoiles

Also, 
at the junction level, let $\tilde{n}_{ST}$ denote the number of passengers following an $ST$-trip. As implied by the end of section (\ref{Line edges, transfer edges and trips}), 
\begin{equation}
\label{equivnntilde}
\tilde{n}_{ST}=\sum_{s\in S}\sum_{t\in T}n_{st} \qquad\qquad\qquad n_{st}=\sum_{ST}\tilde{n}_{ST}\: \delta_{s,\sigma(S,T)}\: \delta_{t,\tau(S,T)}
\end{equation}
Definitions (\ref{edgetrip}) and (\ref{edgetripjunction}) yield
\begin{equation}
\label{equationGG}
x_{ij}=\sum_{st}\chi_{ij}^{st}\:  n_{st}=\sum_{ST}\tilde{\chi}_{ij}^{ST}\:  \tilde{n}_{ST}
\end{equation}
Among the passengers embarking in $i$, some transfer from another line, and some others enter into the network: 
\begin{equation}
\label{entrer}
a_i=z_{\bullet i}+n_{i\bullet}
\end{equation}
where  ``$\bullet$" denotes the summation over the replaced index, as in $n_{i\bullet}=\sum_{j=1}^l n_{ij}$. Similarly, among the passengers disembarking in $i$, some transfer to another line, and some others leave the network: 
\begin{equation}
\label{sortir}
b_i=z_{i\bullet}+n_{\bullet i}
\end{equation}
By construction
\begin{displaymath}
a_{\bullet}=b_{\bullet}=z_{\bullet\bullet}+n_{\bullet\bullet}
\end{displaymath}
where $n_{\bullet\bullet}$ counts the number of passengers, and $z_{\bullet\bullet}$ counts the number of transfers. $z_{\bullet\bullet}/n_{\bullet\bullet}$  is the average number of transfers per passenger.

@@

% if your bibliography is in bibtex format, use those commands:
\bibliographystyle{bmc-mathphys} % Style BST file (bmc-mathphys, vancouver, spbasic).
\bibliography{bmc_article}      % Bibliography file (usually '*.bib' )
% for author-year bibliography (bmc-mathphys or spbasic)
% a) write to bib file (bmc-mathphys only)
% @settings{label, options="nameyear"}
% b) uncomment next line
%\nocite{label}

>>>>

*** Also, 
at the junction level, let $\tilde{n}_{ST}$ denote the number of passengers following an $ST$-trip. As implied by the end of section (\ref{Line edges, transfer edges and trips}), 
\begin{equation}
\label{equivnntilde}
\tilde{n}_{ST}=\sum_{s\in S}\sum_{t\in T}n_{st} \qquad\qquad\qquad n_{st}=\sum_{ST}\tilde{n}_{ST}\: \delta_{s,\sigma(S,T)}\: \delta_{t,\tau(S,T)}
\end{equation}
Definitions (\ref{edgetrip}) and (\ref{edgetripjunction}) yield
\begin{equation}
\label{equationGG}
x_{ij}=\sum_{st}\chi_{ij}^{st}\:  n_{st}=\sum_{ST}\tilde{\chi}_{ij}^{ST}\:  \tilde{n}_{ST}
\end{equation}
Among the passengers embarking in $i$, some transfer from another line, and some others enter into the network: 
\begin{equation}
\label{entrer}
a_i=z_{\bullet i}+n_{i\bullet}
\end{equation}
where  ``$\bullet$" denotes the summation over the replaced index, as in $n_{i\bullet}=\sum_{j=1}^l n_{ij}$. Similarly, among the passengers disembarking in $i$, some transfer to another line, and some others leave the network: 
\begin{equation}
\label{sortir}
b_i=z_{i\bullet}+n_{\bullet i}
\end{equation}
By construction
\begin{displaymath}
a_{\bullet}=b_{\bullet}=z_{\bullet\bullet}+n_{\bullet\bullet}
\end{displaymath}
where $n_{\bullet\bullet}$ counts the number of passengers, and $z_{\bullet\bullet}$ counts the number of transfers. $z_{\bullet\bullet}/n_{\bullet\bullet}$  is the average number of transfers per passenger.

@@

% if your bibliography is in bibtex format, use those commands:
\bibliographystyle{bmc-mathphys} % Style BST file (bmc-mathphys, vancouver, spbasic).
\bibliography{article_tl.bib}      % Bibliography file (usually '*.bib' )
% for author-year bibliography (bmc-mathphys or spbasic)
% a) write to bib file (bmc-mathphys only)
% @settings{label, options="nameyear"}
% b) uncomment next line
%\nocite{label}
